Dynamic Modeling, Parameter Estimation and Uncertainty Analysis in \proglang{R}

### 2019-03-28 article.tex
be consistent

datasheet <- subset(as.data.frame(out),
		    time %in% timesD & name %in% names(observables))
datasheet$sigma <- sqrt(datasheet$value + 1)
datasheet$value <- rnorm(nrow(datasheet), datasheet$value, datasheet$sigma)

>>>>

  datasheet <- subset(as.data.frame(out),
                      time %in% timesD & name %in% names(observables))
  datasheet <- within(datasheet, {
	  sigma <- sqrt(value + 1)
	  value <- rnorm(length(value), value, sigma)
  })
